Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/synthesis.tex
Corrected the last word of the caption of Figure 8 from filter to monitor
Further wordsmithing on the Synthesis section

The verdict of a filter is made and performed within one thread
invocation. Thus, in its given time slice, the filter must complete the
following steps:

@@

\item checks to see if there is any input available; if there is none
then it yields control; otherwise,

\item the input is read (and parsed if need be),

\item the wellformedness predicate is evaluated on the input,

\item if the predicate returns \konst{true} then the input buffer
 is copied to the output; otherwise no action is taken, and

\item the filter yields control.
\end{enumerate}

@@

A monitor may need to accumulate a certain minimum number of
observations before being able to make a meaningful assessment of
behavior. Until that threshold is attained, the monitor is essentially
in a kind of \emph{initialization} phase. In order for correct code to
be generated, monitor specifications need to spell out the values of
output ports when in an initialization phase. For example, suppose a
monitor does some kind of differential assessment of inputs at
adjacent timeslices, alerting when (say) the measured location of a
UAV at times $t$ and $t+1$ is such that the distance between the two
locations is unusually large. Such a monitor needs two measurements
before making its first judgement, but at the time of its first
output, only one measurement will have been made. The specification
must then explicitly state what the correct first output is.

@@

\item Each input is parsed into data of the type specified by the port
  type.

@@

\item Control is yielded.
\end{enumerate}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \scalebox{0.60}{\usebox{\monFn}}
    \end{tabular}
  \end{center}
  \caption{Synthesized CakeML for the filter.}
  \label{fig:monitor-cakeml}
\end{figure}

>>>>

The verdict of a filter is made and performed within one thread
invocation. Thus, in its given time slice, the
following steps must be completed:

@@

\item The filter checks to see if there is any input available.  If there is none
then it yields control; otherwise:

\item The input is read (and parsed if need be);

\item The wellformedness predicate is evaluated on the input;

\item If the predicate returns \konst{true} then the input buffer
 is copied to the output, otherwise no action is taken; and

\item The filter yields control.
\end{enumerate}

@@

A monitor may need to accumulate a certain minimum number of
observations before being able to make a meaningful assessment of
behavior. Until that threshold is attained, the monitor is essentially
in a kind of \emph{initialization} phase. In order for correct code to
be generated, monitor specifications need to spell out the values of
output ports when in an initialization phase. For example, suppose a
monitor does some kind of differential assessment of inputs at
adjacent timeslices, alerting when (say) the measured location of a
UAV at times $t$ and $t+1$ is such that the distance between the two
locations is unusually large. Such a monitor needs two measurements
before making its first judgement, but at the time of its first
output, only one measurement will have been made. The specification
must then explicitly state the correct value for the first output.

@@

\item Each input is parsed into data of the type specified by the port
  type;

@@

\item The monitor yields control.
\end{enumerate}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \scalebox{0.60}{\usebox{\monFn}}
    \end{tabular}
  \end{center}
  \caption{Synthesized CakeML for the monitor.}
  \label{fig:monitor-cakeml}
\end{figure}
